Look, we can do something

### 2024-10-22 paper.tex
Expand introduction

>>>>

In this paper we also use the following common parameters which are used to
describe pore shapes:
\begin{itemize}
\item Convexity $C$ is a relation between surface of a pore and surface bounded
  by its convex hull.
\item Roundness $R$ is a relation between perimeter of a disk which has the same
  surface as a pore to perimeter of that pore.
\item Elongation $E$ is a relation between eigenvalues of a matrix $A$ with the
  smallest and the biggest absolute values. $A$ is a $2 \times 2$ covariation
  matrix of coordinates of pore points. For a discrete image of a pore its
  elements equal to
  \begin{equation*}
    a_{ij} = \sum_{x \in \left\{
      \begin{array}{l}
        \text{Coordinates of points} \\
        \text{belonging to the pore}
      \end{array}
      \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
  \end{equation*}
\end{itemize}
All of these parameters lie in the range $[0, 1]$.
